### 2013-07-06 cws/emnlp_cws/abstract.tex
major revision, mostly complete except for DD description

\begin{abstract}
There are two dominant approaches to the Chinese word segmentation problem: word-based and character-based models, each with respective strengths. Prior work has shown that gains in segmentation performance can be achieved from combining these two types of models; however, 
Past efforts have not provided a practical technique to allow mainstream adoption. We propose a method that effectively combines the strength of both segmentation schemes using an efficient dual-decomposition algorithm for joint inference. Our method is simple and easy to implement. Experiments on SIGHAN 2003 and 2005 evaluation datasets show that our method achieves the best reported results to date on 6 out of 7 datasets.
\end{abstract}

>>>>

\begin{abstract}
There are two dominant approaches to the Chinese word segmentation problem: word-based and character-based models, each with respective strengths. Prior work has shown that gains in segmentation performance can be achieved from combining these two types of models; however, past efforts have not provided a practical technique to allow mainstream adoption. We propose a method that effectively combines the strength of both segmentation schemes using an efficient dual-decomposition algorithm for joint inference. Our method is simple and easy to implement. Experiments on SIGHAN 2003 and 2005 evaluation datasets show that our method achieves the best reported results to date on 6 out of 7 datasets.
\end{abstract}

### 2013-07-06 cws/emnlp_cws/discussion.tex
major revision, mostly complete except for DD description

\section{Discussion}

%In this section we talked about detailed consistency analysis and maybe give some examples.

On the whole, dual decomposition produces state-of-the-art segmentations that are more accurate, more consistent, and more successful at inducing out-of-vocabulary words than the baseline systems that it combines.

\subsection{Dual decomposition convergence}
Plot the histogram of the number of iterations it takes to converge, and percentage of optimality.

\subsection{Consistency}

\cite{Chang:2008:ACL} have shown that increased segmentation consistency is correlated with better machine translation performance. Following their method for calculating the conditional entropy of a segmentation system, we see in Table [insert table] that our dual decomposition method achieves the most consistent segmentations (lowest conditional entropy) on 6 out of 7 datasets.

%
%\subsection{Oracle}
%
%Following \cite{Sun:2010:COLING}, we run an oracle experiment to estimate the upper bound of improvement possible via system combination to further contextualize our results. 
%
%To do so, we combine our two baselines with the gold-standard segmentation. Each character in the test set is labeled with three \emph{B} or \emph{I} tags, \emph{B} when it begins a word and \emph{I} when it is word-medial or word-final, according to our two baselines and the gold standard. We then create oracle labels by majority vote: if the baselines agree, their label is used; if they disagree, the gold label is used.
%
%The results of this oracle experiment, shown in Table [insert table], show that [what do they show? DD approaches the upper bound possible?]
%
%% this is here to know what each column means in the output below
%%=== TOTAL INSERTIONS:	75
%%=== TOTAL DELETIONS:	84
%%=== TOTAL SUBSTITUTIONS:	783
%%=== TOTAL NCHANGE:	942
%%=== TOTAL TRUE WORD COUNT:	11989
%%=== TOTAL TEST WORD COUNT:	11980
%%=== TOTAL TRUE WORDS RECALL:	0.928
%%=== TOTAL TEST WORDS PRECISION:	0.928
%%=== F MEASURE:	0.928
%%=== OOV Rate:	0.022
%%=== OOV Recall Rate:	0.810
%%=== IV Recall Rate:	0.930
%Scoring Oracle Output, Sighan 2003
%for as
%	sighan2003/as.oracle	79	88	173	340	11989	11980	0.978	0.979	0.979	0.071	0.940	0.981
%for cityu
%	sighan2003/cityu.oracle	402	333	893	1628	35087	35156	0.965	0.963	0.964	0.073	0.823	0.976
%for ctb
%	sighan2003/ctb.oracle	929	1014	2504	4447	39921	39836	0.912	0.914	0.913	0.230	0.822	0.939
%for pku
%	sighan2003/pku.oracle	189	190	392	771	17194	17193	0.966	0.966	0.966	0.138	0.925	0.973
%Scoring Oracle Output, Sighan 2003
%for as
%	sighan2005/as.oracle	1876	748	2542	5166	122610	123739	0.973	0.964	0.969	0.099	0.890	0.982
%for cityu
%	sighan2005/cityu.oracle	577	371	1136	2084	40936	41142	0.963	0.958	0.961	0.075	0.839	0.973
%for msr // currently broken
%	sighan2005/msr.oracle	81	107	165	353	10987	10961	0.975	0.978	0.976	0.065	0.934	0.978
%for pku
%	sighan2005/pku.oracle	803	1664	2505	4972	104372	103511	0.960	0.968	0.964	0.124	0.924	0.965
%

\subsection{Error analysis}

>>>>

\section{Discussion and Error Analysis}

On the whole, dual decomposition produces state-of-the-art segmentations that are more accurate, more consistent, and more successful at inducing out-of-vocabulary words than the baseline systems that it combines.
On the SIGHAN 2005 test set, over 99.1\% cases the DD algorithm converged within 100 iterations which gives optimality guarantee. 
In 77.4\% of the cases, DD converged in the first iteration. For the remaining cases, the number of iterations to convergence histogram is plotted in Figure~\ref{fig:histo}.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{histogram.png}
\caption{No. of iterations till DD convergence histogram.}
\label{fig:histo}
\end{center}
\end{figure}

\paragraph{Error analysis}

### 2013-07-06 cws/emnlp_cws/experiment.tex
major revision, mostly complete except for DD description

In this work, we employ two baseline models --- a character-based CRF and a word-based perceptron --- and test the performance of jointly decoding these baseline systems with dual decomposition.

For our character-based CRF, we use the open-source Stanford CRF segmenter described in \cite{Tseng:2005:SIGHAN}.\footnote{http://nlp.stanford.edu/software/segmenter.shtml} In this system we use L2 regularization with a value of X %TODO: insert actual value / word this properly
and sigma set to 3.

For our word-based perceptron, we use a reimplementation of \cite{Zhang:2007:ACL}, run with 10 iterations of training.

For joint decoding with dual decomposition, we use an initial step size set to 0.1, and run for 100 iterations.

% question: what is the relationship between this dev data and that used in sighan2003/2005?
We use the same development set employed by \cite{Zhang:2007:ACL}, with Chinese Treebank sections 1-270, 400-931, and 1001-115 used as training data and sections 271-300 used as development data for tuning the hyperparameters of all three systems.

\subsection{Datasets}
Our test data is the standard SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets. [Add a note here about why not using CTB - who figured out it was broken, how do we know not to use it?]

%List a table of the corpora names, size of training, testing, etc, similar to \cite{Sun:2010:COLING}.

>>>>

\begin{table*}[t]
\centering
\begin{small}
\begin{tabular}{ r | c | c | c | c | c | c | c | c | c | c  }
%\multicolumn{13}{c}{\large{SIGHAN 2005}} \\
\multicolumn{1}{c|}{} & \multicolumn{5}{c|}{AS} &  \multicolumn{5}{c}{PU} \\
\hline
\multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{C$_{\mathrm{onst}}$}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{C$_{\mathrm{onst}}$} \\ 
Char-based CRF    &  95.2 &   93.6  & 94.4  &  58.9 & 0.064  &  94.6 &	95.3 & 94.9  &   77.8   & 0.089    \\
Word-based Perceptron &  95.8 & 95.0 & 95.4  & 69.5 & 0.060  &  94.1 & 95.5  & 94.8  &  76.7 & 0.099     \\ 
Dual-decomp      & 95.9 & 94.9   & {95.4}  & {67.7} & 0.055 & 94.8 & {95.7} & {95.3}  &  {78.7} & 0.086   \\
%\cline{2-9}
\multicolumn{1}{c|}{} &  \multicolumn{5}{c|}{CU} &  \multicolumn{5}{c}{MSR}  \\
\hline
\multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{C$_{\mathrm{onst}}$}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{C$_{\mathrm{onst}}$} \\ 
Char-based CRF    & 94.7 & 94.0 & 94.3  & {76.1}  & 0.065 & 96.4 &   96.6 & 96.5  & 71.3 & 0.074 \\
Word-based Perceptron    & 94.3 & 94.0 & 94.2  & 71.7  & 0.073 &  97.0 &  97.2 & 97.1  & 74.6 & 0.063  \\
Dual-decomp  & {95.0} & 94.4  & {94.7}  & {75.3} & 0.062 &  {97.3} &  {97.4} &  {97.4}  & {76.0} & 0.055  \\
\end{tabular} 
\caption{Results on SIGHAN 2005 datasets. {R$_{\mathrm{oov}}$}  denotes OOV recall, and C$_{\mathrm{onst}}$ denotes segmentation consistency. }\label{tbl:results}
\end{small}
\end{table*}

We conduct experiments  on the SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets to evaluate the effectiveness of the proposed dual-decomposition algorithm. We take the publicly available Stanford CRF segmenter \cite{Tseng:2005:SIGHAN}\footnote{http://nlp.stanford.edu/software/segmenter.shtml} as our character-based baseline model, and reproduce the perceptron-based segmenter from \newcite{Zhang:2007:ACL} as our word-based baseline model.
We adopted the development setting from \cite{Zhang:2007:ACL}, and used CTB sections 1-270 for training, and sections 400-931for development. The optimized hyper-parameters used are: $\ell_{2}$ regularization parameter $\lambda$ in CRF is set to $3$; perceptron is trained for 10 iterations with beam size 200; dual-decomposition is run to max iteration of 100 with initial step size of 0.1. Other than the standard precision (P), recall (R) and F$_1$ scores, we also evaluate segmentation consistency as proposed by \cite{Chang:2008:ACL}. They have shown that increased segmentation consistency is correlated with better machine translation performance. The consistency measure calculates the entropy of segmentation variations -- the lower the score the better.
%List a table of the corpora names, size of training, testing, etc, similar to \cite{Sun:2010:COLING}.

### 2013-07-06 cws/emnlp_cws/introduction.tex
major revision, mostly complete except for DD description

%First paragraph talks about why Chinese Word Segmentation is important.
Chinese text is written without delimiters between words; as a result, Chinese word segmentation (CWS) is an essential foundational step for many tasks in Chinese natural language processing. As demonstrated by [cite, cite, cite - Pichuan, what else?], the quality and consistency of segmentation has important downstream impacts on system performance in machine translation, [and...].

>>>>

%First paragraph talks about why Chinese Word Segmentation is important.
Chinese text is written without delimiters between words; as a result, Chinese word segmentation (CWS) is an essential foundational step for many tasks in Chinese natural language processing. As demonstrated by \cite{Shi:2007:IJCAI,Bai:2008:IJCNLP,Chang:2008:ACL,Kummerfeld:2013:ACL}, the quality and consistency of segmentation has important downstream impacts on system performance in machine translation, POS tagging and parsing.

### 2013-07-06 cws/emnlp_cws/models.tex
a bunch of cleanups and additional writing
major revision, mostly complete except for DD description

\section{Char-based vs. Word-based Segmenters}

\subsection{Char-based models}
Describe models that treat CWS as a character sequence tagging task (first proposed by \cite{Xue:2003:IJCLCLP}), widely adopted and most commonly used these days.
Give the equation of CRF (see \cite{Tseng:2005:SIGHAN}). Briefly describe the features and point out how some of them can be expected to generalize well to OOV words (e.g. suffix and prefix features).

\subsection{Word-based models}
See \cite{Sun:2010:COLING} for a good description. We used the perceptron based model proposed by \cite{Zhang:2007:ACL}, give the equation of the perceptron, and describe the features. Point out how some of these features basically directly capture the training lexicon.

\subsection{Relative Strength and Weakness}
Char-based CRF models are better at generalizing over to OOV words (thus higher OOV recall).  (NOTE: 6 out of 8 datasets on test, CRF has better OOV recall, but we should defer to talk about this in the results section). But as a tradeoff, it generates more inconsistent segmentation, and creates lots of spurious words.
 The advantage of Word-based segmenters are that they are more consistent with the training lexicon, words seen in training lexicon are not likely to be segmented into many new ways; disadvantage is that it doesn't generalize well to OOV. Also exact inference is difficult, need to resolve to approximate decoding algorithms such as beam-searching.

>>>>

\section{Models for CWS}

In this section, we describe the character-based and word-based models we use as baselines, and review existing approaches to combine these models.

\subsection{Character-based Models}
In the most commonly used contemporary approach to character-based segmentation, first proposed by \cite{Xue:2003:IJCLCLP}, CWS is seen as a character sequence tagging task, where each character is tagged on whether it is at the beginning, middle, or end of a word. Conditional random field (CRF) \cite{Lafferty:2001:ICML} is widely adopted for this task, and gives state-of-the-art results \cite{Tseng:2005:SIGHAN}. In a first-order linear-chain CRF model, the conditional probability of a label sequence $\mathbf{y}$ given a word sequence $\mathbf{x}$ is defined as:
\begin{align*}
P(\mathbf{y} | \mathbf{x}) = \frac{1}{Z}{ \sum\limits_{t=1}^{|\mathbf{y}|}{ \exp^{ \vec\theta \vec{f}(x, y_{t}, y_{t+1}) } }}
\end{align*}
\noindent $f(x, y_{t}, y_{t-1})$ are features functions that typically include surrounding n-gram and morphological suffix/prefix features. These types of features capture the compositional properties of characters and are likely to generalize well to unknown words.  
But the Markov assumption in CRF limits the context of such features, it is difficult to capture long-range word features in this model. 
%, which is important for admitting efficient inference, restricts the CRF to very local context features. A first-order CRF can only reason about character boundary decisions of current and neighboring positions. 
%It is therefore difficult to directly model words of greater length. Although higher-order CRF could potentially alleviate this problem, and has been applied to CWS \cite{Zhao:2007:ICNC}, it comes at the cost of exponentially higher model complexity.

\subsection{Word-based Models}
Word-based models searches through lists of word candidates using scoring functions that directly assign scores to word candidates. 
Early word-based segmentation work employed simple heuristics like dictionary-lookup maximum matching \cite{Chen:1992:ACL}. More recent success was reported by  \newcite{Zhang:2007:ACL}, who used a linear discriminative model to score candidate word lists. 
More concretely, given input $\mathbf{x}$, their models seeks for a segmentation $F(\mathbf{x})$ such that $F(\mathbf{x}) =  \argmax{ \vec\alpha \vec\phi(\mathbf{x}) }$.
Feature weights are trained using the average perceptron algorithm \cite{Collins:2002:EMNLP}. Searching through the entire  search space $\mathrm{GEN}(\mathbf{x})$ is intractable even with a local model. A beam-search algorithm is therefore employed. The search algorithm consumes one character input token at a time, and iterate through the existing beams to score two new alternative hypothesis by either appending the new character to the last word in the beam, or start a new word at current position.

\subsection{Combine Models with Dual-decomposition} 
Various mixing approaches have been proposed to combine the above two approaches \cite{Wang:2006:SIGHAN,Lin:2009:CICLing,Sun:2009:HLT-NAACL,Sun:2010:COLING,Wang:2010:COLING}. 
These mixing models perform well on standard datasets, but are not in wide use because of their high computational costs and difficulty of implementation.

Dual decomposition offers an attractive framework for combining these two types of models without incurring high cost in model complexity (in contrast to \cite{Sun:2009:HLT-NAACL}) or decoding efficiency (in contrast to bagging in \cite{Wang:2006:SIGHAN,Sun:2010:COLING}).
DD has been successfully applied to similar situations where we want to combine local model with global models, for example, in dependency parsing \cite{Koo:2010:EMNLP}), bilingual sequence tagging \cite{Wang:2013:ACL} and word alignment \cite{Denero:2011:ACL}.

Give a brief description of DD algorithm, focus on the intuition. See \cite{Wang:2013:ACL} and \cite{Denero:2011:ACL} for a good short introduction example.
Refer users to \cite{Rush:2012:JAIR} for a full tutorial on dual decomp.
The modification to Viterbi decoding is exactly the same as in \cite{Wang:2013:ACL} and \cite{Denero:2011:ACL}. The modification to the beam-search is similar, each time we extend a hypothesis with a new character, depending if the new character is appended to the last word or starting a new word, the corresponding DD penalty is factored into the score for the new hypothesis.
